The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-06-30 brains-protocol.tex
fix/methods: some better phrasings

We could therefore study the individual transformation process at work when authors alter quotations, by examining the modified words in each transformation.
\newtext{Since our approach is exploratory however, we do not know at the outset which precise effect of cognitive bias we are looking for.
Indeed the data we use does not come from a controlled experiment in the laboratory, designed to elicit a particular effect: they are recordings of real life interactions going on every day, with all the complexity and uncertainty of conditions that this entails.
In this first study, therefore, we did not try to predict and explain in detail the cognitive processes responsible for transformations, as this would be akin to a drink from the firehose.
Our goal, instead, is to show that such effects exist and are measurable even if they are part of a larger complexity, that is, we aim to prove first a relatively weak hypothesis before trying stronger ones.
If this is confirmed, we will have successfully applied laboratory analyses to out-of-laboratory data, opening a path to explanations of actual (\hbox{vs.} simulated) cultural evolution with tools from cognitive science.
As explained in the previous section, this is the reason we chose to use measures that can aggregate over all the transformations in the data set.}

\newtext{With this goal of keeping} the analysis \newtext{tractable}, we focused on quotation transformations consisting in the \emph{substitution} of a word by another word (and only those cases) in order to unambiguously discuss single word replacements.
\newtext{This restriction also allows us to more reliably infer the information that is missing in our data set, as explained further down (see "Substitution model").}
To quantify those substitutions we decided to associate a number of features to each word, the variation of which we can statistically study.

>>>>

We could therefore study the individual transformation process at work when authors alter quotations, by examining the modified words in each transformation.
\newtext{Since our approach is exploratory however, we do not know at the outset which precise effect of cognitive bias we are looking for.
Indeed the data we use does not come from a controlled experiment in the laboratory, designed to elicit a particular effect: they are recordings of real life interactions, with all the complexity and uncertainty of conditions this entails.
In this first study, therefore, we did not try to predict and explain in detail the cognitive processes responsible for transformations, as this would be akin to a drink from the firehose.
Our goal, instead, is to show that such effects exist and are measurable, even if they are part of a larger complexity.
That is, we aim to prove first a relatively weak hypothesis before trying stronger ones.
If this is confirmed, we will have successfully applied laboratory analyses to out-of-laboratory data, opening a path to explanations of actual (\hbox{vs.} simulated) cultural evolution with tools from cognitive science.
As explained in the previous section, this is the reason we chose to use measures that can aggregate over all the transformations in the data set.}

To keep the analysis \newtext{tractable}, we focused on quotation transformations consisting in the \emph{substitution} of a word by another word (and only those cases) in order to unambiguously discuss single word replacements.
\newtext{This restriction also allows us to more reliably infer the information that is missing in our data set, as explained further down (see "Substitution model").}
To quantify those substitutions we decided to associate a number of features to each word, the variation of which we can statistically study.
